Prospective testing for the prevalence or transience of a shock effect before it occurs

### 2021-09-13 prevalence_testing/postshocktest2021draft.tex
minor changes to model formulation

  \; f(\mc{F}_{i,t},\alpha_i) = \alpha_i g(t) +  \sum_{j=1}^{\tilde q_{1}}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{\tilde q_2-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]

@@

$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,\t q_{i,1}})'$, 
$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i,\t q_{i,2}})'$, 
$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,q_3})'$, 

@@

  \tilde{\mathbf{\phi}}_{i,j} &= \mu_{\tilde{\mathbf{\phi}}_j} + \lambda_{i,j}, j = 1,\ldots, \t q_{i,1}, \; \text{where} \; \lambda_{i,j} \overset{ind}{\sim} \mathcal{F}_{\lambda}(\x_{i,T_i^*}) \; \text{with} \; |\mu_{\tilde{\mathbf{\phi}}_j}| < 1 \; \text{and} \; |\mu_{\tilde{\mathbf{\phi}}_j} + \lambda_{i,j}| < 1,  \\
  \tilde{\mathbf{\theta}}_{i,j} &= \theta_{i,j} + \gamma_{i,j}, j = 1,\ldots,\t q_{i,2}, \; \text{where} \; \gamma_{i,j} \simiid \mathcal{F}_{\gamma} \; \text{with} \; \mrm{E}_{\mathcal{F}_{\gamma}}(\gamma_i) = \beta_o + \beta\mbf{x}_{i,T_i^*+1}, \mrm{Var}_{\mathcal{F}_{\gamma}}(\gamma_i) = \Sigma^2_\gamma,  \\  
  \t q_{i,k} &\overset{ind}{\sim} \mathcal{F}_k(\x_{i,T_i^*}), \; k = 1,2, \\

@@

\tilde{\mathbf{\phi}}_i \indep \lambda_{i,j} \indep \gamma_i \indep \mathbf{\delta}_i \indep \t q_{i,k} \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i,t},

@@

where the distribution $\mathcal{F}_k(\x_{i,T_i^*})$ is a discrete distribution conditional on $\x_{i,T_i^*}$, $\theta_{i,j} = 0$ for any $q_1 < j \leq \t q_{i,1}$, and $\phi_{i,j} = 0$ for any $q_2 < j \leq \t q_{i,2}$. The model \eqref{model-gen} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}. \textbf{Need to carefully show}. Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in 
$\mathcal{F}_k(\x_{i,T_i^*})$ and $\mathcal{F}_{\lambda}(\x_{i,T_i^*})$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\mu_\alpha +\delta_i'\x_{i,T_i^*}$ and $\beta_o + \beta\mbf{x}_{i,T_i^*+1}$ respectively.

>>>>

  \; f(\mc{F}_{i,t},\alpha_i) = \alpha_i +  \sum_{j=1}^{q_{1}}\t\phi_{i,j}y_{i, t-j} + \sum_{j=0}^{q_2-1}\t\theta_{i,j+1}'\mbf{x}_{i,t-j}, \\[.2cm]

@@

$\tilde{\mathbf{\phi}}_i = (\t\phi_{i,1},\ldots,\t\phi_{i,q_{1}})'$, 
$\tilde{\mathbf{\theta}}_i = (\t\theta_{i,1},\ldots,\t\theta_{i, q_{2}})'$, 
$\mathbf{\delta}_i = (\delta_{i,1},\ldots,\delta_{i,p})'$, 

@@

  \tilde{\mathbf{\phi}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{i,T_i^*+1}) \; \text{where} \; |\tilde{\mathbf{\phi}}_{i,j}| < 1,  \\
  \tilde{\mathbf{\theta}}_{i,j} &= \theta_{i,j} + \gamma_{i,j}, j = 1,\ldots, q_{2}, \; \text{where} \; \gamma_{i,j} \simiid \mathcal{F}_{\gamma} \; \text{with} \; \mrm{E}_{\mathcal{F}_{\gamma}}(\gamma_i) = \beta_o + \beta\mbf{x}_{i,T_i^*+1}, \mrm{Var}_{\mathcal{F}_{\gamma}}(\gamma_i) = \Sigma^2_\gamma,  \\  
 % \t q_{i,k} &\overset{ind}{\sim} \mathcal{F}_k(\x_{i,T_i^*}), \; k = 1,2, \\

@@

\tilde{\mathbf{\phi}}_i \indep \lambda_{i,j} \indep \gamma_i \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i,t},

@@

where the distribution $\mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{i,T_i^*+1})$ exists between -1 and 1 and $\mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{i,T_i^*+1})) - \mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}}(\x_{j,T_i^*+1})) \to 0$ as $\|\x_{i,T_i^*+1} - \x_{j,T_i^*+1}\| \to 0$.
%the distribution $\mathcal{F}_k(\x_{i,T_i^*})$ is a discrete distribution conditional on $\x_{i,T_i^*}$, $\theta_{i,j} = 0$ for any $q_1 < j \leq \t q_{i,1}$, and $\phi_{i,j} = 0$ for any $q_2 < j \leq \t q_{i,2}$. 
The model \eqref{model-gen} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}. \textbf{Need to carefully show}. Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in $\mathcal{F}_{\tilde{\mathbf{\phi}}}$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\mu_\alpha + \delta_i'\x_{i,T_i^*}$ and $\beta_o + \beta\mbf{x}_{i,T_i^*+1}$ respectively.
